### 2010-04-27 VerboseNotes.tex
cheatsheet拡充
git-svn-id: https://dav.misho-web.com/svn/cyghome/trunk/QFT/CheatSheet@383 c04c31ef-c4f7-4b37-ba94-86ebe2b9c820

%#!latexmk CheatSheet.tex
%%% Time-Stamp: <2010-03-25 01:33:22 misho>
\section{Verbose Notes}
\subsection{Spinor Fields}
\subsubsection{Lorentz group and Lorentz algebra}
\begin{tabular}{l@{ :\ \ \ }l}
Metric &  $\eta^\% = \diag(+1, -1, -1, -1),\qquad \eta^\# = \diag(-1,+1,+1,+1).$\\
Lorentz transf. in $\mathbb R^{1,3}$ & Linear transf. $x^\mu \mapsto \Lambda\T^\mu_\nu x^\nu$ which conserve $x^2$.\\
 & \then $\Hrsd = \Hmnd \Lambda\T^\mu_\rho \Lambda\T^\nu_\sigma.$
 and form a group $L$.\\[.8zw]

Disconnected parts of $L$ &
  $L_0 := \left\{ \det\Lambda = +1 \land \Lambda\T_0^0 >0\right\} \quad
   L_P := \left\{ \det\Lambda = -1 \land \Lambda\T_0^0 >0\right\}$\\
& $L_T := \left\{ \det\Lambda = +1 \land \Lambda\T_0^0 <0\right\} \quad
   L_{PT} := \left\{ \det\Lambda = -1 \land \Lambda\T_0^0 <0\right\}$\\
& \qquad ($L_0$ is identical with $\%\gSO(1,3) / \#\gSO(3,1)$. )\\[1zw]

@@

Generators &
 $x'^\mu =  x^\mu + \epsilon\T^\mu_\nu x^\nu
   =: \left(\delta^\mu_\nu\mp\frac\ii2\epsilon_{\rho\sigma}(J^{\rho\sigma})\T^\mu_\nu\right)x^\nu$
   \quad with $J^{\rho\sigma} = -J^{\sigma\rho}$\\
&\then 
$ (J_{\rho\sigma})\T^\mu_\nu = \mp\ii\left(
                                     \delta^\mu_\rho\Hsnd-\delta^\mu_\sigma\Hrnd
                                    \right),$\\
Lorentz algebra & therefore
 $[J_{\mu\nu},J_{\rho\sigma}] = \pm\ii(
    \Hmrd J_{\nu\sigma} + \Hnsd J_{\mu\rho} - \Hmsd J_{\nu\rho} - \Hnrd J_{\mu\sigma})$\\
\end{tabular}

@@

\subsection{Weyl Spinor}
Now we introduce Weyl spinors. First, I de
%%% Local Variables:
%%% TeX-master: t
%%% End:

>>>>

%#!latexmk CheatSheet.tex
%%% Time-Stamp: <2010-04-27 22:42:12 misho>
\section{Verbose Notes}
\subsection{Spinor Fields}
\subsubsection{Lorentz group and Lorentz algebra}
\begin{tabular}{l@{ :\ \ \ }l}
Metric &  ${\RED\eta} = \diag(+1, -1, -1, -1),\qquad {\BLUE \eta} = \diag(-1,+1,+1,+1).$\\
Lorentz transf. in $\mathbb R^{1,3}$ & Linear transf. $x^\mu \mapsto \Lambda\T^\mu_\nu x^\nu$ which conserve $x^2$.\\
 & \then $\Hrsd = \Hmnd \Lambda\T^\mu_\rho \Lambda\T^\nu_\sigma.$
 and form a group $L$.\\[.8zw]

Disconnected parts of $L$ &
  $L_0 := \left\{ \det\Lambda = +1 \land \Lambda\T_0^0 >0\right\} \quad
   L_P := \left\{ \det\Lambda = -1 \land \Lambda\T_0^0 >0\right\}$\\
& $L_T := \left\{ \det\Lambda = +1 \land \Lambda\T_0^0 <0\right\} \quad
   L_{PT} := \left\{ \det\Lambda = -1 \land \Lambda\T_0^0 <0\right\}$\\
& \qquad ($L_0$ is identical with ${\RED\gSO(1,3)} / {\BLUE\gSO(3,1)}$. )\\[1zw]

@@

Generators &
 $x'^\mu =  x^\mu + \epsilon\T^\mu_\nu x^\nu
   =: \left(\delta^\mu_\nu\mp\frac\ii2\epsilon_{\rho\sigma}(J^{\rho\sigma})\T^\mu_\nu\right)x^\nu$
   \quad with $J^{\rho\sigma} = -J^{\sigma\rho}$\\
&\then 
$ (J_{\rho\sigma})\T^\mu_\nu = \pm\ii\left(
                                     \delta^\mu_\rho\Hsnd-\delta^\mu_\sigma\Hrnd
                                    \right),$\\
Lorentz algebra & therefore
 $[J_{\mu\nu},J_{\rho\sigma}] = \mp\ii(
    \Hmrd J_{\nu\sigma} + \Hnsd J_{\mu\rho} - \Hmsd J_{\nu\rho} - \Hnrd J_{\mu\sigma})$\\
\end{tabular}

@@

\subsection{Weyl Spinor}

%%% Local Variables:
%%% TeX-master: t
%%% End:
